---
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MEA-single-electrode-barchart}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
library(MEAanalysis)
knitr::opts_knit$set(root.dir = '..')
```

# Export Electrode Burst Files from AxIS Navigator 3.6.2 software

The following vignette describes the workflow used to analyse Axion Biosystems MEA recordings and export the associated electrode burst csv files for use in the MEAanalysis package. 

1) Load your Axion Biosystems MEA recording into the AxIS Navigator 3.6.2 software (click file, click open recordings, navigate to your recording and click open).

2) Right click the chosen recording in the 'Streams' panel and click configuration. Select the spontaneous and viability configuration.

3) Right click the Spike Detector and selective an Adaptive Threshold Crossing of 6x standard deviation.

4) Right click the Burst Detector (ISI) and set the Maximum Inter-Spike Interval to 100 mS and the Minimum Number of Spikes to 5.

5) On the recording panel, ensure that 'Electrode Burst List' is selected in the Burst Detector (ISI) selection box.

6) Click record. Once the recording is complete the electrode burst list file will be exported to the same file directory as the recording. This can be used as an input to the MEAanalysis create_electrode_dataset and create_synchrony_dataset functions.




